\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}

\title{Minutes of Meeting}
\date{\today}

\begin{document}

\maketitle

\begingroup
\large
\textbf{Attendees:} John, Steve, Sam, Julie
\endgroup

\subsection{Sam's Minutes}
\author{Luca Spiteri (Steve)}

\subsubsection{Action Items}
\textbf{First 48 Hours}
- Meeting with Steve; business vision and current actions \\
- Meeting with the team; establish rapport \\
- Begin analyzing the current state of the business \\

\textbf{First Week}
- Team Meetings; understand challenges and ideas \\
- Observe the day to day sales physical in stores \\
- Identify minor adjustments, not too many changes \\

\textbf{First Month}
- Short-term goals; measurable goals \\
- Meetings with Computer Engineering department, celebrating sucesses to create unity \\

\textbf{First 6 Months}
- Develop Talent as proposed to Steve;
- Streamline operations on the already established system \\

\textbf{First Year}
- Self development in the business acumen as discussed with Steve \\
- Openness and transparency with board meetings \\


\subsubsection{Discussion}
\begin{itemize}
    \item Steve asked how Sam will balance consulting the team and making final decisions without delay.
    \item Sam plans to use a democratic leadership approach, involving the team in decision-making to drive enthusiasm and morale.
    \item Ultimately, Sam will make the final decision, considering the team's input.
    \item Julie inquired about maintaining ongoing communication.
    \item Sam's 6-month plan includes setting up a talent team to guide decisions with market insights.
    \item Steve questioned how Sam will maintain company culture.
    \item Sam believes his people skills align with the company culture and plans to develop his business acumen further.
    \item Sam and Julie discussed how they could handle the departemental meetings. Even delegating some weeks to departemental heads that could report back to them.
\end{itemize}

\subsubsection{Requests}
\begin{itemize}
    \item Funding for the talent team.
    \item Steve stated that this would be a investment worth looking into.
    \item Possiblilty to expand into online stores.
    \item John states that in this time of change it would be a good idea to look into this.
\end{itemize}

\subsection{John's Minutes}
\author{Graham Pellegrini (Sam)}

\subsubsection{Action Items}

\begin{itemize}
    \item \textbf{First 48 Hours:}
    \begin{itemize}
        \item Assess Julie and Sam's performance metrics for their respective divisions, focusing on immediate team feedback to address concerns about leadership styles.
        \item Request a summary of divisional goals from Steve, highlighting alignment with CompChimp's long-term strategic vision.
    \end{itemize}
    \item \textbf{First Week:}
    \begin{itemize}
        \item Convene a meeting with Julie to discuss her team's feedback and explore methods to incorporate team input into her decision-making process while maintaining agility.
        \item Hold a similar session with Sam to encourage more confident, independent decision-making while retaining his collaborative approach.
        \item Review Steve’s quarterly report outlining progress in mentoring Julie and Sam.
    \end{itemize}
    \item \textbf{First Month:}
    \begin{itemize}
        \item Implement anonymous surveys across both divisions to gauge employee morale, satisfaction, and engagement levels.
        \item Establish quarterly leadership workshops for Julie and Sam, focusing on transformational leadership and conflict resolution skills.
    \end{itemize}
    \item \textbf{Six Months:}
    \begin{itemize}
        \item Review division performance metrics, including sales growth, product innovation timelines, and employee retention rates.
        \item Conduct a mid-year evaluation of Steve’s mentorship impact on Julie and Sam’s readiness for increased responsibilities.
    \end{itemize}
    \item \textbf{One Year:}
    \begin{itemize}
        \item Present a detailed evaluation of Julie and Sam’s leadership development and performance at the annual board meeting.
        \item Facilitate discussions on the succession plan, including the possibility of promoting one of them to CEO while retaining mentorship from Steve.
    \end{itemize}
\end{itemize}

\subsubsection{Discussion}

\begin{itemize}
        \item Steve acknowledged Julie’s decisiveness but emphasized the need for her to engage her team more to maintain morale and encourage innovation.
        \item He suggested that Sam focus on setting clear boundaries for consultation and decision-making to strengthen his leadership presence.
    \end{itemize}
    \begin{itemize}
        \item Sam highlighted that Julie’s directive style might lead to long-term resistance among her team members, which could affect productivity.
        \item He proposed that she consider delegating decision-making authority in areas where team members excel.
    \end{itemize}
    \begin{itemize}
        \item Julie pointed out that Sam’s consultative style could delay decisions critical to sales momentum. She encouraged him to balance input with timely action.
        \item She recommended that he practice making smaller, independent decisions to build confidence.
    \end{itemize}
    \begin{itemize}
        \item Introduce a peer mentorship system between Sam and Julie, allowing them to learn from each other’s strengths and address weaknesses collaboratively.
        \item Assign trial projects requiring both decisive action and team collaboration to refine their leadership approaches.
    \end{itemize}

\subsubsection{Request}

\begin{itemize}
    \item Approve funding for quarterly leadership workshops tailored to developing Julie and Sam’s transformational leadership capabilities.
    \item Allocate resources for anonymous team surveys to track morale and engagement consistently.
    \item Extend Steve’s mentorship role for an additional year to guide Julie and Sam through their leadership transition, with a performance review at month 18 to decide on future senior management structures.
\end{itemize}


\subsection{Steve's Minutes}
\author{Bahne Thiel-Peters (Julie)}

\subsubsection{Action Items}

\subsubsubsection{First 48 Hours}
\begin{itemize}
    \item Familiarize with the company culture and structure.
    \item Meet key personnel and establish rapport.
    \item Identify immediate operational issues requiring attention.
\end{itemize}

\subsubsubsection{First Week}
\begin{itemize}
    \item Familiarize with the company culture and structure.
    \item Meet key personnel and establish rapport.
    \item Identify immediate operational issues requiring attention.
\end{itemize}

\subsubsubsection{First Month}
\begin{itemize}
    \item Implement a formal review system to track divisional progress.
    \item Introduce any necessary structural adjustments.
    \item Conduct regular meetings with Sam and Julie to clarify responsibilities and foster open communication.
\end{itemize}

\subsubsubsection{First Six Months}
\begin{itemize}
    \item Set measurable milestones for Sam and Julie with a focus on outcomes.
    \item Facilitate team-building activities to encourage collaboration across departments.
    \item Closely monitor performance and provide guidance to align divisional efforts with company objectives.
\end{itemize}

\subsubsubsection{First Year}
\begin{itemize}
    \item Review progress toward strategic objectives and make necessary adjustments.
    \item Conduct a formal evaluation of Sam and Julie’s leadership, incorporating feedback from their teams.
\end{itemize}

\subsubsubsection{First Two Years}
\begin{itemize}
    \item Ensure divisions have sustainable growth strategies and clearly defined goals.
    \item Introduce initiatives to reward cross-departmental collaboration, supporting long-term stability.
\end{itemize}

\subsubsection{Discussion}
\subsubsubsection{Steve's Plan}
\begin{itemize}
    \item Emphasis on building rapport and understanding team dynamics.
    \item Long-term focus on sustainability and collaboration across divisions.
    \item Monitoring strategy praised for balance and structure.
\end{itemize}

\subsubsubsection{Critiques}
\begin{itemize}
    \item John Expressed concern over potential delays in immediate outcomes due to mediation-centric approaches.
    \item Julie suggested considering additional metrics in the scorecard for dynamic business environments.
\end{itemize}

\subsubsection{Requests}
\subsubsubsection{From Steve:}
\begin{itemize}
    \item Approval to introduce structured team-building initiatives within the first six months.
    \item Feedback on the proposed balanced scorecard metrics and inclusion of qualitative KPIs.
\end{itemize}

\subsubsubsection{From Sam and Julie:}
\begin{itemize}
    \item Agreement on clear boundaries for resource use, including meeting room allocation.
    \item Support for resolving overlapping operational areas to reduce tension.
\end{itemize}

\subsubsubsection{From John:}
\begin{itemize}
    \item Comprehensive evaluation of Sam and Julie at month 12 to determine leadership capabilities.
    \item Proposal for a mid-year check-in to assess Steve’s performance as CEO.
\end{itemize}

\subsection{Julie's Minutes}
\author{Phileas Barome (John)}

\subsubsection{Action Items}

\subsubsubsection{First 48 Hours}
\begin{itemize}
    \item Meet Key Team Members.
    \item Review Current Projects and Finances.
    \item Identify Immediate Risks and Opportunities
\end{itemize}

\subsubsubsection{First Week}
\begin{itemize}
    \item Introduce \textit{weekly standup meetings} to get to know peoples strengths and characteristics.
    \item Set team expectations and define goals.
\end{itemize}

\subsubsubsection{First Month}
\begin{itemize}
    \item Address initial inefficiencies discovered in the first week.
    \item Draft a basic roadmap for expanding the engineering division’s offerings.
    \item Work closely with Sam’s team in Computer Sales to identify areas where the Engineering Division can support increased sales or product offerings.
    \item Build Team Morale by starting events after the work or on weekends.

\end{itemize}

\subsubsubsection{First Six Months}
\begin{itemize}
    \item Launch a New Tech Innovation Hub within the Division, to introduce new technologies.
    \item Rethink and eventually refine Division Structure and Roles.
    \item Monitor Performance Closely. What's with the previously made goals from the last months?
\end{itemize}

\subsubsubsection{First Year}
\begin{itemize}
    \item Review steps from the first half year.
    \item Solidify Division Strategy and Vision: Develop a long-term strategy for the Computer Engineering Division.
    \item Implement Key Structural Changes: Formalize and optimize the organizational structure within the division - clear reporting lines and job descriptions. 
\end{itemize}

\subsubsection{Discussion}

\begin{itemize}
    \item Sam criticized Julie's leadership, highlighting her challenges with social interactions as a potential obstacle to effective team management.
    \item John stressed the need for Julie and Sam to collaborate to align their divisions.
\end{itemize}

\subsubsection{Requests}

\begin{itemize}
    \item Request \textit{funding for research and development}, enabling the Engineering Division to stay competitive and expand into new areas. 
    \item Request \textit{support for training programs} or hiring additional staff with specialized skills.
    \item Request board approval for organizational changes to support team growth.
\end{itemize}

\end{document}
